On Secure Delegation of SampBQP with a Classical Client

### 2020-03-23 qpip.tex
Handle mixed states in QPIP1 SampBQP

	Now, for the other case, $j\notin J$.
	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
	we then have
	\Ethan{$\rho_j$ isn't a pure state, so need to rewrite this using traces and such}
	$$\braket{\rho_j|H_{C'(x)}|\rho_j}<\poly(\varepsilon).$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
	$$\braket{\rho_j|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
	By a standard fidelity argument, the measurement results on $\rho_j$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.

>>>>

	Now, for the other case, $j\notin J$.
	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2h\Rightarrow\tr\left(H_{C'(x)}\rho_j\right)<\poly(\varepsilon)$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$
